%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Ankur Sharma
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Ankur}{Sharma}{ \urlstyle{same}\url{https://bigdata.uni-saarland.de/people/sharma.php} \\
\href{mailto:ankur.sharma@bigdata.uni-saarland.de}{ankur.sharma@bigdata.uni-saarland.de} | (+49) 17 33 00 771
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Saarland University}
\descript{Ph.D. Student}
\location{Oct 2014 - now \\ Big Data Analytics Group \\ Saarbruecken, Germany}
\sectionsep


\subsection{TU Dresden}
\descript{Visiting Student, ZIH}

\location{May 2013 - Sept 2014 \\ Dresden, Germany}
\sectionsep

\subsection{NIT Sikkim}
\descript{B.Tech. in Computer Science}
\location{Aug 2010 - Sept 2014 \\ Ravangala (Sikkim), India}
\location{ Cum. GPA: 9.15/10.00 \\ Institute/Department Gold Medals}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/sh-ankur/}{\custombold{sh-ankur}} \\
LinkedIn://  \href{https://www.linkedin.com/in/ankursh92}{\custombold{ankursh92}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Graduate}
Distributed Systems \\
Operating Systems \\
Database Systems\\
Compiler Construction \\
Optimization \\
\sectionsep

\subsection{Undergraduate}
Mobile Computing \\
Internet \& Web Apps \\
Compiler/Interpreter\\
Data Structure \& Algorithms\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{5000 lines:}
C++ \textbullet{}   GO \textbullet{} Java \textbullet{} Python \\
\location{\~ 1000 lines:}
C \textbullet{} BASH \textbullet{} Javascript \\
\location{Familiar:}
GIT \textbullet{} SVN \textbullet{} SQL \textbullet{} Spark  \textbullet{} Flink
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
2014 \textbullet{}  Graduate Fellowship \\
2014 \textbullet{}  Undergraduate Gold Medals \\
2013 \textbullet{} DAAD WISE Fellowship \\
2012 \textbullet{} IITB Research Fellowship
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{ChainifyDB}
\descript{Transaction Processing in Blockchain Systems}
\location{Jan 2019 – Present | Under Submission at SIGMOD'2020}
We are developing a platform that is capable of transforming an existing Database Infrastructure in a B2B setup into a Blockchain Infrastructure. The goal of this project is to make the blockchain technology usable without actually adding an all-new blockchain infrastructure into the business's technology stack.
\sectionsep

\runsubsection{Fabric++}
\descript{Transaction Processing in Blockchain Systems}
\location{Jan 2018 – Oct 2018 | Published at SIGMOD'2019}
We integrated MVCC and TransactionReordering in Hyperledger Fabric, which improved transaction throughput by more than 12x for the highly contended workload.
\sectionsep

\runsubsection{AnKerDB}
\descript{Hybrid OLTP/OLAP Processing}
\location{Apr 2016 – Dec 2017 | Published at PVLDB'2016 and SIGMOD'2018}
We implemented an efficient mechanism (user-level and inside the Linux) to snapshot the virtual memory area, which is used to extend MVCC to support efficient analytical/transactional workload in main-memory database systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\vspace*{0.8cm}
\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
\bibliographystyle{unsrt}
\bibliography{publications}
\nocite{*}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Saarland University}
\descript{Research Assistant}
\location{April 2016 - Present | Saarbruecken, Germany}
%\vspace{\topsep}
Developing technology for efficient transaction processing and memory management in Database Systems and Permissioned Blockchain Systems.
\sectionsep

\runsubsection{TU Dresden}
\descript{Undergraduate Research Assistant}
\location{May 2013 - Sep 2014 | Dresden, Germany}
Developed methods for performance analysis and optimization of HPC applications.
\sectionsep

\runsubsection{IIT Bombay}
\descript{Undergraduate Research Intern}
\location{May 2012 - Jul 2012 | Mumbai, India}
Developed lightweight java-based XML parser for in-house Android applications used at IIT Bombay.

\end{minipage} 
\end{document}